Recursive Neural Network Part-of-Speech Tagger

### 2013-12-21 paper/paper.tex
Add citation.

\subsubsection{AdaGrad}
We used the AdaGrad online learning method to train our model. Let $\theta$ be a vector of all parameters needed to train in RNN model and $\theta_t$ means the parameter vector before training on $t_{th}$ example. And let  $g_{t,i}$ to be the gradient value of $i_{th}$ parameter on $t_{th}$ example. Then the AdaGrad is just updating the parameter vector by
$$\theta_{{t+1},i} = \theta_{{t},i}  - \frac{\alpha}{\sqrt{\sum_{s=1}^t \theta_{{s},i}^2 }} g_{t,i}$$,
where the $\alpha$ is a constance to set the scale of learning rate.

>>>>

\subsubsection{AdaGrad}
We used the AdaGrad online learning method to train our model (Socher et al., 2013). Let $\theta$ be a vector of all parameters needed to train an RNN model and $\theta_t$ means the parameter vector before training on the $t$-th sentence. And let  $g_{t,i}$ to be the gradient value of $i_{th}$ parameter on $t$-th sentence. Then the AdaGrad is just updating the parameter vector by
$$\theta_{{t+1},i} = \theta_{{t},i}  - \frac{\alpha}{\sqrt{\sum_{s=1}^t \theta_{{s},i}^2 }} g_{t,i}$$,
where the $\alpha$ is a constance to set the scale of learning rate.
